Extended Data

### 2021-09-17 doc/manuscript/Dow_Extended_Data.Rmd
cleanup

## table captions
species_table_caption <-"Extended Data Table 1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
sample_size_by_year_caption <- "TO BE REMOVED | Sample size by year "
mean_growth_parameters_caption = "Extended Data Table 2 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest. "
tree_ring_summary_caption =  "Extended Data Table 3 | Summary of tree-ring data and analysis ( including species, n chronologies (= n sites), n positively correlated with April T, n sig.)"

>>>>

## table captions
species_table_caption <-"Extended Data Table 1 | Dominant ring- and diffuse-porous species at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest, along with sample sizes included in this analysis."
mean_growth_parameters_caption = "Extended Data Table 2 | Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest."
tree_ring_summary_caption =  "Extended Data Table 3 | Summary of tree-ring data and analysis ( including species, n chronologies (= n sites), n positively correlated with April T, n sig.)"
